First steps in synthetic algebraic geometry

### 2017-03-18 snippets/qcoh.tex
Weaker and more natural condition

\begin{scholium}\label{scholium}
Let~$E \in \Zar(S)$ be a quasicoherent~$\affl$-module.
Let~$A \in \Zar(S)$ be a quasicoherent~$\affl$-algebra such that~$\Spec(A) \in
\Zar(S)$ is representable by an object of the site used to define~$\Zar(S)$.
% XXX: "locally representable"?
Then the canonical morphism
\[ E \otimes_\affl A \longrightarrow [\Spec(A), E] \]
is an isomorphism.
\end{scholium}

@@

\begin{rem}The condition in Scholium~\ref{scholium} that~$\Spec(A)$ is
representable by an object of the site used to define~$\Zar(S)$ cannot be
dropped. For instance, if we employ the parsimonious sites and consider~$S =
\Spec \ZZ$,~$E = \affl$, and $A = \K_S^\Zar$ (where~$\K_S$ is the sheaf of
rational functions on~$S$, which in this case is the constant sheaf~$\ul{\QQ}$),
then~$\Spec(A)$ is the functor of points of the~$\ZZ$-scheme~$\Spec(\QQ)$.
This functor coincides with the functor of points of the empty~$\ZZ$-scheme on
the parsimonious sites; therefore~$\Spec(A) = \emptyset$ from the internal point
of view. Thus the codomain of the canonical morphism is the zero algebra, but the
domain is not.
\end{rem}

>>>>

\begin{scholium}\label{scholium}
Let~$E \in \Zar(S)$ be a quasicoherent~$\affl$-module.
Let~$A \in \Zar(S)$ be a quasicoherent~$\affl$-algebra such that~$\Spec(A) \in
\Zar(S)$ is representable by an object of the site used to define~$\Zar(S)$.
Then the canonical morphism
\[ E \otimes_\affl A \longrightarrow [\Spec(A), E] \]
is an isomorphism.
\end{scholium}

@@

\begin{rem}The condition in Scholium~\ref{scholium} that~$\Spec(A)$ is
representable by an object of the site used to define~$\Zar(S)$ is slightly
unnatural from a topos-theoretic point of view, since the conclusion of the
Scholium depends only on the topos over the site and not the site itself.
In fact, the condition can be weakened and made more natural at the
same time: It suffices to require that~$\Spec(A)$ is \emph{locally}
representable by an object of the site.

However, the condition can't be dropped completely. For instance, if we employ the
parsimonious sites and consider~$S = \Spec \ZZ$,~$E = \affl$, and $A =
\K_S^\Zar$ (where~$\K_S$ is the sheaf of rational functions on~$S$, which in
this case is the constant sheaf~$\ul{\QQ}$), then~$\Spec(A)$ is the functor of
points of the~$\ZZ$-scheme~$\Spec(\QQ)$. This functor coincides with the
functor of points of the empty~$\ZZ$-scheme on the parsimonious sites;
therefore~$\Spec(A) = \emptyset$ from the internal point of view. Thus the
codomain of the canonical morphism is the zero algebra, but the domain is not.
\end{rem}
